\documentclass[12pt]{letter}

% \usepackage[britdate]{canterbury-letter}
\usepackage[britdate]{SU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{Postdoctoral fellow}
\department{Department of Ecology, Environment, and Plant Sciences (DEEP)}
\location{Stockholm University}
\cityzip{Stockholm, Sweden}
\telephone{}
\fax{}
\email{alyssa.cirtwill@liu.se}
\url{http://cirtwill.github.io}
\name{Dr. Alyssa R. Cirtwill}

\newcommand{\myjournal}{\emph{Ecology Letters}}

\begin{document}

\begin{letter}{\bf Professor Rob Freckleton\\
               Executive Editor, Methods in Ecology and Evolution\\
               Department of Animal and Plant Sciences\\
               University of Sheffield\\
               Sheffield S10 2TN, UK
                               }

% Borrowing heavily from the proposal

\opening{Dear Prof. Freckleton:}

    My co-authors and I are pleased to resubmit our manuscript 
    MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. Dr. Aaron Ellison, Senior Editor, noted that the Associate Editor and four reviewers ``\emph{recognise a kernel of important work in this manuscript}" but that a significant shift in emphasis was necessary for this kernel to shine through. We believe that this revision has addressed the Associate Editor's and Reviewers' concerns and that our manuscript is clearer and more polished as a result. We thank them for their careful feedback.


    Note that we uploaded an earlier version of this manuscript to biorXiv \\(doi: \emph{https://doi.org/10.1101/332536}). We have uploaded a copy of this version as CI\_preprint.pdf. The present version has been substantially re-organised and contains additional material not included in the pre-print.


    We appreciate the opportunity to resubmit our manuscript and thank you for your continued consideration. We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution} because of the general nature of uncertainty around interactions and the broadly-applicable solution we offer. We are confident that our worked example and easy-to-use scripts will provide a useful template for empiricists and theoreticians alike. We hope that you agree and eagerly await your reply.


\closing{Best regards,}


\end{letter}
\end{document}


% Suggested reviewers:

% Pedro Jordano pedroj@me.com Estacion Biologica de Donana CSIC

% Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC) 

% Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg - co-author with DG in 2016

% Paulo Guimaraes prguima@gmail.com Universidade de Sao Paola

% Jason Tylianakis jason.tylianakis@canterbury.ac.nz :) - co-author with DG in 2016

% Owen Petchey University of Zurich owen.petchey@ieu.uzh.ch

% Eve McDonald-Madden e.mcdonaldmadden@uq.edu.au University of Queensland

% Laura Burkle laura.burkle@montana.edu Montana State University Dept. of Ecology - co-author with DG in 2017

% Jane Memmott jane.memmott@bristol.ac.uk University of Briston, School of Biological Sciences

% Sonia Kefi sonia.kefi@umontpellier.fr Institut des Sciences de l'Evolution de Montpellier co-author with DG in 2017, 2016; co-author with AE in 2017

% Charles Godfray charles.godfray@zoo.ok.ac.uk Oxford, Dept. of Zoology

% Catherine Graham catherine.graham@wsl.ch Swiss Federal Research Institute (WSL) - co-ahtour with DG in 2018, TR in 2018

% Extra suggestions
% Jacopo Grilli jgrilli@santafe.edu Santa Fe Institute
% Ben Weinstein Oregon State University weinsteb@oregonstate.edu
% Jean-Philippe Lessard Concordia University jp.lessard@concordia.ca
% Catherine Graham catherine.graham@wsl.ch Swiss Federal Research Institute WSL 
% Anne Chao chao@stat.nthu.edu.tw National Tsing Hua University
% Robert Colwell robertkcolwell@gmail.com Museum of Natural History, University of Colorado Boulder
% Mari Moora mari.moora@ut.ee (as working on fungal interaction networks, but being well on the map)
% (Anna Traveset atraveset@uib.es )
% Ignasi Bartomeus nacho.bartomeus@gmail.com 
% Owen Lewis owen.lewis@zoo.ox.ac.uk



